AHABus \& FCORE:\\Modular Bus for High-Altitude Balloon Missions

### 2017-04-09 chapters/03-methodology.tex
Add Aknowledgements
Better table styles
Start of discussion

\subsection{Protocol Specification}

@@

To avoid possible byte order conflicts between the architectures used on the
flight platform and the ground station, multi-bytes values referred to in the
specification should always be transmitted as big-endian (most significant byte
first).

@@

The start sequence design had to be changed to occupy a single frame byte, as
opposed to two bytes in version 2 of the frame format. Using a single byte to
detect the start of a frame was not deemed sufficient, since the probably of
that exact value occurring elsewhere in the binary stream would have been
fairly high. To mitigate this, the third and final version of the frame format
uses a single frame start marker (\texttt{0x5A}) at the beginning of each
frame, and each frame must be preceded by at least one synchronisation byte
(\texttt{0xAA}), inserted in the binary stream as shown in the lower half of 
figure \ref{fig:frame-sync-extra}. The following 223 bytes in the frame
(starting with the protocol version number) are error-corrected, with the
frame's 32 trailing bytes.

@@

\subsection{Protocol Specification}

@@

\subsection{Hardware Prototype}

@@

\subsubsection{Mission Design and Configuration Files}

@@

\section{Testing}
\label{sec:testing}

\subsection{Component Testing}

\subsection{Integrated Testing}

\subsubsection{Day in the life Testing}

\subsubsection{Resilience Testing}

>>>>

\subsection{AHABus Radio Protocol}

@@

To avoid possible byte order conflicts between the architectures used on the
flight platform and the ground station, multi-byte values referred to in the
specification should always be transmitted as big-endian (most significant byte
first).

@@

The start sequence design had to be changed to occupy a single frame byte, as
opposed to two bytes in the second version of the frame format. Using a single
byte to detect the start of a frame was not deemed sufficient, since the
probably of that exact value occurring elsewhere in the binary stream would
have been fairly high. To mitigate this, the third and final version of the
frame format uses a single frame start marker (\texttt{0x5A}) at the beginning
of each frame, and each frame must be preceded by at least one synchronisation
byte (\texttt{0xAA}), inserted in the binary stream as shown in the lower half
of figure \ref{fig:frame-sync-extra}. The following 223 bytes in the frame
(starting with the protocol version number) are error-corrected, with the
frame's 32 trailing bytes.

@@

\subsection{AHABus Payload Bus Protocol}

@@

\subsection{Hardware Prototype}
\label{sec:flight-hardware}

@@

\subsubsection{Mission Design and Configuration Files}
\label{sssec:conf-file}

@@

\section{Evaluation}
\label{sec:testing}

\subsection{Day in the life Testing}
\label{ssec:method-ditl}

\subsection{Resilience Testing}
\label{ssec:method-resilience}

### 2017-04-09 chapters/05-discussion.tex
Add Aknowledgements
Start of discussion

\section{Introduction}

@@

\subsection{Overview}

@@

\subsection{Radio System Stress Tests}

>>>>

The aim of the project was to design and build a prototype of a High-Altitude
Balloon modular platform, similar in principle to buses used in the satellite
industry, and evaluate both the feasibility of such a platform and its
performance. The platform was required to allow for stable internal
communications between the payloads and the \acrlong{obc}, tracking of
ancillary data (\acrshort{gnss} co-ordinates and altitude) and reliable
transmission of the collected telemetry to one or multiple ground stations 
through a low-power radio channel. In this chapter, the \acrshort{ahabus}
platform prototype is evaluated against these aims, first qualitatively through
general observations and critical analysis, then in quantitatively, using the
testing results presented in chapter \ref{ch:results}. This chapter finally
presents the further work that would be required for the platform to fully meet
its design goals.

@@

\subsection{Platform}

As a software platform, the \acrshort{ahabus} prototype fulfils most of its
goals: the flight \acrshort{fcore} was complete enough to support full-flight
simulations, manage the bus, \acrshort{gnss} and radio communications without
failure. During the testing phase, no major software design error were found,
and the only instances where failures were found to be caused by the flight
software itself. Though quite cumbersome to work with, and lacking in
documentation, the \acrshort{fcore} configuration tool discussed in section
\ref{sssec:conf-file} proved reliable, and the resulting \acrshort{fcore} builds
did not suffer from erroneous bandwidth usage.

There are, however, areas that could be improved upon: the software design of
\acrshort{fcore} makes use of numerous data buffers for the different
transmission layers. Those buffers are required because of the slow speeds that
those communications protocol use, but are at the moment not optimised to be as
small as required – instead, all buffers can hold \SI{4096}{\byte}. This would
prevent the current source code to be ported to architectures that provide less
dynamic memory than the chosen ESP8266 micro-controller does.

Due to lack of time, very little work was done on the hardware aspect of
\acrshort{ahabus}: testing was done using a development board instead of the
bare micro-controller for the \acrlong{obc}, and the power and payload bus were
little more than wires routed through a breadboard. An improved development
platform using a printed circuit board was designed as presented in
\ref{sec:flight-hardware}, but could not be fully assembled and tested in time.

@@

\subsection{Radio System Resilience Tests}
